---
title: "Section 8"
date: "October 23, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Paired Code Review

Now that it's been a few weeks since you've worked on PS3, it would be a good exercise to see how quickly you can remember your line-of-thought when writing the code.  Find a partner (preferably someone you haven't worked with before).  Pull up problem set 3 (extracting Shakespeare's work).  For the first 10 minutes, have one partner read over the code for extracting chunks, speakers, number of acts, and number of scenes from the play.  The other partner should be available for questions during this time.  After 10 minutes, switch roles.  Consider the following when reading each others' code:

* Is it clear within 10 seconds (either through style or commenting) what each chunk of code does?
* Is the overall strategy for extraction clear?
* Regular expressions are in general hard to make clear given their concise nature.  Is it clear from the style or commenting what each expression is trying to do?

## Lazy Evaluation

Without running the code below, can you guess the output of the expressions at the end of the chunk?  Also, why are two sets of parentheses necessary?

```{r, eval = FALSE}
x <- 10

lazy <- function(x=0) {
  y <- 2
  z <- 3
  w <- x + y + z
  x <- 1
  return(w)
}

lazy2 <- function(x=0) {
  y <- 2
  z <- 3
  w <- x + y + z
  g <- function() w
  x <- 1
  return(g)
}

lazy3 <- function(x=0) {
  y <- 2
  z <- 3
  delayedAssign("w", x + y + z)
  g <- function() w
  x <- 1
  return(g)
}

lazy4 <- function(x=0) {
  y <- 2
  z <- 3
  g <- function() x + y + z
  x <- 1
  return(g)
}

lazy5 <- function(x) {
  y <- 2
  z <- 3
  g <- function() w
  w <- x + y + z
  return(g)
}

lazy6 <- function(x) {
  y <- 2
  z <- 3
  g <- function() x + y + z
  return(g)
}

lazy()
lazy2()()
lazy3()()
lazy4()()
lazy5(x)()
lazy6(x)()

lazy7 <- lazy5(x)
lazy8 <- lazy6(x)
lazy9 <- lazy6(x)
lazy9()
rm(x)
lazy7()
lazy8()
lazy9()
```

## Practice

Write a function `new_counter()` the creates a closure which counts the number of times it has been called.  For example, you should be able to do:

```{r, eval = F}
counter1 <- new_counter()
counter2 <- new_counter()
```

```{r, eval = F}
counter1()
#[1] 1
counter1()
#[1] 2
counter1()
#[1] 3
counter2() # This is a different counter
#[1] 1
```

Write a function `delayed_by(t, f)` that admits two arguments `t`, time in milliseconds and `f`, any function.  It should return a modified copy of `f` that runs `t` milliseconds slower.

